\documentclass[11pt,a4paper,sans]{moderncv}

%% ModernCV themes
\moderncvstyle{casual}
\moderncvcolor{blue}
\renewcommand{\familydefault}{\sfdefault}
\nopagenumbers{}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}


\firstname{Sebastian}
\familyname{Lenartowicz}
\title{ Problem Solver}
\address{21 Kearney Street}{Guelph, ON N1E 7H2}
\mobile{(519)~400~8185}
\email{slenarto@mail.uoguelph.ca}
\social[github]{github.com/NGTOne}
\quote{What needs doing today?}

\begin{document}
\makecvtitle

\section{Education}
\cventry{2011--2016 (anticipated)}{Bachelor of Computing}{University of Guelph}{Guelph, ON}{}{Degree in Computer Science with minor in Geographical Information Systems (GIS).}
\cventry{Graduated 2011}{OSSD}{John F. Ross Collegiate Vocational Institute}{Guelph, ON}{}{Graduated with awards in business and computer science.}

\section{Skills and Experience}
\subsection{Projects}
\cvitem{Open-source Project}{Created an MIT-licensed open-source library for research into hierarchical genetic algorithms.}
\cvitem{Computational Cluster}{Created and benchmarked a 12-node heterogenous Beowulf cluster using throwaway computers.}
\cvitem{E-Textbook}{Developed interactive e-textbook for course on Visual Basic software development, now in use at alma mater.}

\subsection{Software Development}
\cvlistitem{Ability to learn new languages, frameworks, and methodologies quickly on demand.}
\cvlistitem{Thorough knowledge of C, C++, and Java.}
\cvlistitem{Working knowledge of bash shell script, Perl, Python, SQL, and LaTeX.}
\cvlistitem{Significant understanding of Linux systems and POSIX standard.}
\cvlistitem{Experience with Linux kernel and kernel development.}
\cvlistitem{Experience with git and subversion (SVN) version control systems.}
%%\cvlistitem{Basic familiarity with JNI (Java Native Interface) and JDBC (Java DataBase Connectivity).}

\subsection{Operating Systems and Productivity Software}
\cvlistitem{Significant background with Linux systems at the user level, primarily Ubuntu and Debian.}
\cvlistitem{Substantial experience with Windows XP and higher, and some knowledge of Windows 95 and higher.}
\cvlistitem{Experience with Cygwin (open-source POSIX system emulator for Windows).}
\cvlistitem{Thorough knowledge of Microsoft Office 2003, 2007, and 2011, including but not limited to Word, Excel, OneNote, Outlook, and Powerpoint.}

\newpage
\section{Work Skills}
\cvlistitem{Fast learner, especially in regards to software development and new software.}
\cvlistitem{Significant ability for analysis of systems and their components.}
\cvlistitem{Tenacious, especially when there is a challenge.}
\cvlistitem{Ability to keep meticulous records and documentation, in order to more efficiently correct problems in the future and enable others to do the same.}
\cvlistitem{Experience in explaining technology, both hardware and software, to laypersons.}
\cvlistitem{Ability to communicate well, both orally and in written format.}

\section{Experience}
\cventry{May--August 2014}{Intern}{Wind River Systems}{Kanata, ON}{}{Second work term on OVP project.
\begin{itemize}
\item Developed automated build system using bash shell scripts to produce operating system images for testing.
\item Integrated Future Aerospace Capabilities Environment (FACE) conformance test suite into product and tested conformance of Wind River Linux to FACE standard.
\item Continued to maintain BitBake-based build system and components of OVP v6.0.
\item Increased knowledge of Linux kernel and inner workings.
\end{itemize}}

\cventry{September--December 2013}{Intern}{Wind River Systems}{Kanata, ON}{}{Intern and general developer on OVP (Open Virtualization Profile) project.
\begin{itemize}
\item Assisted with development of OVP v5.0.1 prior to public release.
\item Maintained BitBake-based Linux build management system.
\item Added new packages and functionality to OVP.
\item Maintained upstream open-source projects.
\item Gained familiarity with Linux kernel and git source control system.
\end{itemize}}

\section{References}
References available upon request.

\end{document}